Notes on $\etarho$

### 2008-08-20 docs/eta_notes/paper.tex
added a flow chart of when eta quantities are created and used

\def\etarho     {\eta_\rho}
\def\etarhocc   {\etarho^{\rm cc}}
\def\divetarho  {\nabla\cdot(\etarho\eb_r)}

@@

\maketitle

We carry around three different quantities: $\etarho$ (edge-centered), $\etarhocc$ (cell-centered), and $\divetarho$ (edge-centered).  These are each 1D in the radial direction.  These notes discuss when each of these is used, and how they are computed, in both plane-parallel and spherical.

\section{Computing $\etarho, \etarhocc$, and $\divetarho$}
This is done in {\tt make\_eta.f90}.
\subsection{Plane-Parallel}
We first compute a radial edge-centered multifab, $\eta_{\rho}^{\rm flux}$, using
\begin{equation}
\eta_{\rho,\ib+\half\eb_r}^{\rm flux} = \Ub_{\ib+\half\eb_r}^{n+\half} \rho_{\ib+\half\eb_r}^{n+\half} - w_{0,r+\half}^{n+\half}\rho_{0,r+\half}^{n+\half, {\rm pred}}
\end{equation}
$\etarho$ is the edge-centered ``average'' value of $\eta_{\rho}^{\rm flux}$,
\begin{equation}
\eta_{\rho,r+\half} = \overline{\eta_{\rho,\ib+\half\eb_r}^{\rm flux}}
\end{equation}
$\etarhocc$ is a cell-centered average of $\etarho$,
\begin{equation}
\eta_{\rho,r}^{\rm cc} = \frac{\eta_{\rho,r+\half} + \eta_{\rho,r-\half}}{2}.
\end{equation}
$\divetarho$ is the cell-centered divergence of $\etarho$,
\begin{equation}
\left[\divetarho\right]_r = \frac{\eta_{\rho,r+\half} - \eta_{\rho,r-\half}}{\Delta r}.
\end{equation}
\subsection{Spherical}

>>>>

\def\etarho     {\eta_\rho}
\def\etarhocc   {\etarho^{\rm cc}}
\def\etarhoflux {\etarho^{\rm flux}}
\def\divetarho  {\nabla\cdot(\etarho\eb_r)}

@@

\maketitle
\tableofcontents
\clearpage

We carry around three different 1D radial quantities: $\etarho$ (edge-centered), $\etarhocc$ (cell-centered), and $\divetarho$ (edge-centered).  These notes discuss when each of these is used, and how they are computed, in both plane-parallel and spherical.

\section{Flow Chart}
\begin{enumerate}
\item Enter {\tt advance} with $[\etarho, \etarhocc, \divetarho]^{n-\half}$.
\item Call {\tt make\_w0}.  The spherical version uses uses $\etarho$ and $\etarhocc$.
\item Call {\tt density\_advance}.  The plane-parallel version computes $\etarhoflux$.
\item Call {\tt correct\_base}, which uses $\divetarho$.
\item Compute $[\etarho, \etarhocc, \divetarho]^{n+\half,*}$.
\item Call {\tt make\_psi}.  The plane-parallel version uses $\etarhocc$.
\item Call {\tt make\_w0}.  The spherical version uses uses $\etarho$ and $\etarhocc$.
\item Call {\tt density\_advance}.  The plane-parallel version computes $\etarhoflux$.
\item Call {\tt correct\_base}, which uses $\divetarho$.
\item Compute $[\etarho, \etarhocc, \divetarho]^{n+\half}$.
\item Call {\tt make\_psi}.  The plane-parallel version uses $\etarhocc$.
\end{enumerate}

\section{Computing $\etarho, \etarhocc$, and $\divetarho$}
This is done in {\tt make\_eta.f90}.
\subsection{Plane-Parallel}
We first compute a radial edge-centered multifab, $\eta_{\rho}^{\rm flux}$, using
\begin{equation}
\eta_{\rho,\ib+\half\eb_r}^{\rm flux} = \Ub_{\ib+\half\eb_r}^{n+\half} \rho_{\ib+\half\eb_r}^{n+\half} - w_{0,r+\half}^{n+\half}\rho_{0,r+\half}^{n+\half, {\rm pred}}
\end{equation}
$\etarho$ is the edge-centered ``average'' value of $\eta_{\rho}^{\rm flux}$,
\begin{equation}
\eta_{\rho,r+\half} = \overline{\eta_{\rho,\ib+\half\eb_r}^{\rm flux}}
\end{equation}
$\etarhocc$ is a cell-centered average of $\etarho$,
\begin{equation}
\eta_{\rho,r}^{\rm cc} = \frac{\eta_{\rho,r+\half} + \eta_{\rho,r-\half}}{2}.
\end{equation}
$\divetarho$ is the cell-centered divergence of $\etarho$,
\begin{equation}
\left[\divetarho\right]_r = \frac{\eta_{\rho,r+\half} - \eta_{\rho,r-\half}}{\Delta r}.
\end{equation}
\subsection{Spherical}
\section{Using $\etarho$}
\subsection{Plane-Parallel}
NOT USED.
\subsection{Spherical}
In {\tt make\_w0}
\section{Using $\etarhocc$}
\subsection{Plane-Parallel}
In {\tt make\_psi}
\subsection{Spherical}
In {\tt make\_w0}
\section{Using $\divetarho$}
\subsection{Plane-Parallel}
In {\tt correct\_base}
\subsection{Spherical}
In {\tt correct\_base}
